\hypertarget{intro}{%
\subsection{Intro}\label{intro}}

A Hardware Description Language(HDL) is purely that. It merely describes
hardware. There are a couple types of HDLs, digital and
mixed(digital+analog). This tutorial deals with digital HDLs.

HDLs aren't very useful by themselves. Typically, they might be passed
to a synthesizer which reduces the HDL into a gate list that describes
all the connections between various gates. A gate list is more commonly
known as a netlist.

There are different kinds of synthesizers. Some synthesizer frameworks
target FPGAs while others target physical fabrication or VLSI. In VLSI,
HDL is just the first step in a long laborious sequence of tasks that
usually results in a finished physical chip.

After writing some HDL, you may wish to know whether or not it does what
you want. This can be accomplished using an HDL simulator. Currently,
the only Free and Open Source(FOSS) VHDL simulator being maintained is
\href{https://ghdl.readthedocs.io}{GHDL}.

\hypertarget{installing-ghdl}{%
\subsection{Installing GHDL}\label{installing-ghdl}}

\hypertarget{ubuntu}{%
\subsubsection{Ubuntu}\label{ubuntu}}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{sudo}\NormalTok{ apt update}
\FunctionTok{sudo}\NormalTok{ apt install build{-}essential gnat git llvm clang zlib1g{-}dev}
\FunctionTok{mkdir}\NormalTok{ {-}p \textasciitilde{}/src}\KeywordTok{;} \BuiltInTok{cd}\NormalTok{ \textasciitilde{}/src}
\FunctionTok{git}\NormalTok{ clone https://github.com/ghdl/ghdl}
\BuiltInTok{cd}\NormalTok{ ghdl}
\FunctionTok{mkdir}\NormalTok{ build}\KeywordTok{;} \BuiltInTok{cd}\NormalTok{ build}
\ExtensionTok{../configure}\NormalTok{ {-}{-}with{-}llvm{-}config {-}{-}prefix=/usr/local}
\FunctionTok{make}\NormalTok{ {-}j8}
\FunctionTok{sudo}\NormalTok{ make install}
\end{Highlighting}
\end{Shaded}

\hypertarget{macos}{%
\subsubsection{MacOS}\label{macos}}

\hypertarget{installing-homebrew-package-manager}{%
\paragraph{Installing HomeBrew package
manager}\label{installing-homebrew-package-manager}}

first you should check if you have brew so in the terminal type
\texttt{\$brew}

If that command returns,

\texttt{-bash:\ brew:\ command\ not\ found}

you don't have brew. So do the following:

\begin{Shaded}
\begin{Highlighting}[]
\ExtensionTok{/usr/bin/ruby}\NormalTok{ {-}e }\StringTok{"}\VariableTok{$(}\ExtensionTok{curl}\NormalTok{ {-}fsSL https://raw.githubusercontent.com}
\ExtensionTok{/Homebrew/install/master/install}\VariableTok{)}\StringTok{"}
\end{Highlighting}
\end{Shaded}

\hypertarget{installing-ghdl-on-mac}{%
\subsubsection{Installing GHDL on Mac}\label{installing-ghdl-on-mac}}

\begin{Shaded}
\begin{Highlighting}[]
\ExtensionTok{brew}\NormalTok{ install wget}
\FunctionTok{mkdir}\NormalTok{ {-}p \textasciitilde{}/src}\KeywordTok{;} \BuiltInTok{cd}\NormalTok{ \textasciitilde{}/src}
\FunctionTok{wget}\NormalTok{ https://github.com/ghdl/ghdl/releases/download/v0.36/ghdl{-}0.36{-}macosx{-}llvm.tgz}
\FunctionTok{mkdir}\NormalTok{ {-}p ghdl}
\FunctionTok{tar}\NormalTok{ {-}C ghdl {-}xf ghdl{-}0.36{-}macosx{-}llvm.tgz}
\FunctionTok{rm}\NormalTok{ ghdl{-}0.36{-}macosx{-}llvm.tgz}
\BuiltInTok{cd}\NormalTok{ ghdl/bin}
\BuiltInTok{echo} \StringTok{"export PATH=}\DataTypeTok{\textbackslash{}"}\KeywordTok{\textasciigrave{}}\BuiltInTok{pwd}\KeywordTok{\textasciigrave{}}\StringTok{:}\DataTypeTok{\textbackslash{}$}\StringTok{PATH}\DataTypeTok{\textbackslash{}"}\StringTok{"} \OperatorTok{>>}\NormalTok{ \textasciitilde{}/.bash\_profile}
\end{Highlighting}
\end{Shaded}

\hypertarget{windows}{%
\subsubsection{Windows}\label{windows}}

Install \texttt{bash\ for\ windows} on windows and follow the
instructions above for Ubuntu.

\hypertarget{verifying-installation}{%
\subsection{Verifying Installation}\label{verifying-installation}}

Open up a new terminal and do \texttt{ghdl\ -\/-help}. You should see a
list of some ghdl commands and their explanations.
